Open-Source Web-Based Visualizer for \\ Dynamic-Response Shared Taxi Simulations

### 2020-12-30 src/paper.tex
first version w screenshots

[[PIC OF ANIMATION OR TWO ]]

@@

Difference plots are also generated for some scenarios, especially comparing the DRT scenarios to the "base case" depicting current conditions.

@@

@@

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.4\textwidth}
   \includegraphics[width=\linewidth]{images/fig-drt-vehicles.png}
   \caption{DRT vehicles and routes}
   \label{fig:vehicles}
\end{subfigure}
\begin{subfigure}[c]{0.4\textwidth}
   \includegraphics[width=\linewidth]{images/fig-drt-flyovers.png}
   \caption{DRT passenger origins and destinations}
   \label{fig:flyover}
\end{subfigure}
\caption{Dynamic Response Transit (DRT) animation screenshots}
\end{figure}

@@

Difference plots compare the DRT scenarios to the "base case" depicting current conditions.

\begin{figure}[ht]
  \centering
  \begin{subfigure}[c]{0.32\textwidth}
     \includegraphics[width=\linewidth]{images/fig-link-vols.png}
     \caption{DRT Vehicle volumes, daily aggregation }
     \label{fig:vehicles}
  \end{subfigure}
  \begin{subfigure}[c]{0.32\textwidth}
     \includegraphics[width=\linewidth]{images/fig-mode-share.png}
     \caption{Mode shift, example DRT alternative vs. base case}
     \label{fig:flyover}
  \end{subfigure}
  \caption{Dynamic Response Transit (DRT) further visualization examples}
\end{figure}

@@

\small{

@@

}
